### 2019-11-12 thesis.tex
*** empty log message ***

\chapter{Kinetic theory of plasmas}
\label{cha:kin-theo}

@@

\chapter{Microscopic equations for a fully ionized plasma}
\label{appF}
Plasmas are ionized gases that exhibit collective behavior. Usually composed
of positive and negative charges and neutral particles, a plasma is said to
be \emph{neutral} when the quantity of particles with opposite charges is the
same~\cite{klimo}, and \emph{nonneutral} when it is constituted - or have a
significant excess - of one kind of charge~\cite{DavidsonNonNeutral}. In this
work, it will be considered a fully ionized hydrogen plasma, which is overall
neutral, with the number of protons and electrons being the same.

Electrons and ions are sources of electric and magnetic fields. Due to the
long-range nature of these fields, particles can interact simultaneously, at
distance, with several other particles in the system. The effective range of
the interactions among charges is determined by the \emph{Debye length}
\begin{equation}
  \label{debye}
  \lambda_{De}=\sqrt{\frac{T_a}{4\pi n_a e_a^2}},
\end{equation}
where $a=i$ for ions and $a=e$ for electrons. This means that a specific charge
will interact effectively only with other charges that are inside of a virtual
sphere with radius given by $\lambda_{De}$, being almost completely shielded
from the influence of particles outside the \emph{Debye sphere}. I say almost
because there are small fluctuations in the \emph{Debye shielding}; they are
behind the complex self-consistent collective behavior of plasmas.

Such characteristic ads a layer of complexity in the plasma dynamics, that does
not exists in the description of neutral gases. For instance, the microscopic
state of a plasma is not

>>>>

\chapter{Kinetic theory of plasmas}
\label{cha:kin-theo}
Plasmas are ionized gases that exhibit collective behavior. Usually composed
of positive and negative charges and neutral particles, a plasma is said to
be \emph{neutral} when the quantity of particles with opposite charges is the
same~\cite{klimo}, and \emph{nonneutral} when it is constituted - or have a
significant excess - of one kind of charge~\cite{DavidsonNonNeutral}. In this
work, it will be considered a fully ionized hydrogen plasma, which is overall
neutral. In such case, the density of protons and electrons per volume unity
is the same, therefore $n_e=n_i=n$.

Electrons and ions are sources of electric and magnetic fields. Due to the
long-range nature of these fields, particles can interact simultaneously, at
distance, with several other particles in the system. The effective range of
the interactions among charges is determined by the \emph{Debye length}
\begin{equation}
  \label{debye}
  \lambda_{De}=\sqrt{\frac{k_BT_e}{4\pi n e^2}},
\end{equation}
where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
the plasma density and $e$ the charge. This means that a specific charge
will interact effectively only with other charges that are inside of a
virtual sphere with radius given by $\lambda_{De}$, being almost completely
shielded from the influence of particles outside the \emph{Debye sphere}.

@@

\chapter{Microscopic equations for a fully ionized plasma}
\label{appF}
Plasmas are ionized gases that exhibit collective behavior. Usually composed
of positive and negative charges and neutral particles, a plasma is said to
be \emph{neutral} when the quantity of particles with opposite charges is the
same~\cite{klimo}, and \emph{nonneutral} when it is constituted - or have a
significant excess - of one kind of charge~\cite{DavidsonNonNeutral}. In this
work, it will be considered a fully ionized hydrogen plasma, which is overall
neutral, with the density of protons and electrons being the same, therefore
$n_e=n_i=n$.

Electrons and ions are sources of electric and magnetic fields. Due to the
long-range nature of these fields, particles can interact simultaneously, at
distance, with several other particles in the system. The effective range of
the interactions among charges is determined by the \emph{Debye length}
\begin{equation}
  \label{debye}
  \lambda_{De}=\sqrt{\frac{k_BT_e}{4\pi n e^2}},
\end{equation}
where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
the plasma density and $e$ the charge. This means that a specific charge
will interact effectively only with other charges that are inside of a
virtual sphere with radius given by $\lambda_{De}$, being almost completely
shielded from the influence of particles outside the \emph{Debye sphere}.
